Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-01-04 paper.tex

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Our dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control ({\it e.g.}, airbag control), health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor model, during simulation; however, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting legacy designs (usually written in low-level languages). The present paper discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent model checking application.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous, in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance, and in cyber-physical systems (CPS), which demand short development cycles and again high-level of reliability~\cite{leeCPS}. As a consequence, human life has also become more and more dependent on the services provided by this type of system and, in particular, their success depends both on the provided service relevance and quality.

@@

Besides, when physical interaction with the real world is needed, which happens in CPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to computer processors, are enabling system designers to move more features to software, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered during verification~\cite{Kroening15}.

@@

This position paper tackles four major problems in computer-aided verification for embedded systems: (RP1) providing suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs; (RP2) exploiting SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving; (RP3) proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware; and (RP4) incorporating knowledge about system purpose and associated features, which aims to detect system-level failures.

@@

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control ({\it e.g.}, airbag control), health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor model, during simulation; however, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting legacy designs (usually written in low-level languages). The present paper discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent model checking application.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous, in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance, and in cyber-physical systems (CPS), which demand short development cycles and again high-level of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on the services provided by this type of system and, in particular, their success is strictly related to both provided service relevance and quality.

@@

Besides, when physical interaction with the real world is needed, which happens in CPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models.

A number of distinctive characteristics might influence the embedded system development and verification process, which include: mass production and static structure, functionality determined by software in read-only memory, multi-core processors with scalable shared memory, and limited amount of energy. Additionally, the increasing computational power and decreasing size and cost, which are common to the area of computer processors, are enabling system designers to move more features to software, which consequently leads to difficulties in verifying design correctness, since stringent constraints imposed by the underlying hardware ({\it e.g.}, real-time, memory allocation, interrupts, and concurrency) must be considered during verification~\cite{Kroening15}.

@@

This position paper tackles four major problems in computer-aided verification for embedded systems: (RP1) providing suitable encoding into the Satisfiability Modulo Theories (SMT) \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs, (RP2) exploiting SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving, (RP3) proving correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware, and (RP4) incorporating knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

@@

\bibitem{leeCPS2}
Lee E.:
\newblock {\em The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}. 
\newblock In: Sensors 15(3): pp. 4837--4869, 2015.
